### 2014-07-22 Docs/mg/mg.tex
more MG docs

The following smoothers are available (but not necessarily for both the
cell-centered and nodal solvers):
\begin{itemize}
\item {MG\_SMOOTHER\_GS\_RB}: a red-black Gauss-Seidel smoother

\item {MG\_SMOOTHER\_JACOBI}: a Jacobi smoother (not implemented for 
the dense nodal stencil)

\item {MG\_SMOOTHER\_MINION\_CROSS}

\item {MG\_SMOOTHER\_MINION\_FULL}

\item {MG\_SMOOTHER\_EFF\_RB}
\end{itemize}

@@

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 0: smoothing only.

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 1: biconjugate
  gradient stabilized---this is the default.

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 2: conjugate
  gradient method

\item {\tt mg\_bottom\_solver} / {hg\_bottom\_solver} = 4: a special 
  bottom solver that extends the range of the multigrid coarsening
  by aggregrating coarse grids on the original mesh together and
  further coarsening. \MarginPar{does this option then use bicg 
  at the new bottom?}

@@

@@

\item {\tt stencil\_fill\_cc\_all\_mglevels} / {\tt stencil\_fill\_cc}:

\item {\tt ml\_cc}:

  \item {\em recursively descend V-cycle}
\MyArrow[1em]{start1}{end1}{colorii,line width=2pt}
  \begin{itemize} 
  \item \tikzmark{end1} {\tt cc\_mg\_tower\_smoother}:

  \item {\tt compute\_defect}:

  \item\tikzmark{start1} {\tt ml\_restriction}:
  \end{itemize}

  \item {\tt mg\_tower\_bottom\_solve}:

\end{itemize}
\item multiple {\tt compute\_defect} calls:

>>>>

The following smoothers are available (but not necessarily for both the
cell-centered and nodal solvers):
\begin{itemize}
\item {\tt MG\_SMOOTHER\_GS\_RB}: a red-black Gauss-Seidel smoother

\item {\tt MG\_SMOOTHER\_JACOBI}: a Jacobi smoother (not implemented for 
the dense nodal stencil)

\item {\tt MG\_SMOOTHER\_MINION\_CROSS}

\item {\tt MG\_SMOOTHER\_MINION\_FULL}

\item {\tt MG\_SMOOTHER\_EFF\_RB}
\end{itemize}

@@

\item {\tt mg\_bottom\_solver} / {\tt hg\_bottom\_solver = 0}: smoothing only.

\item {\tt mg\_bottom\_solver} / {\tt hg\_bottom\_solver = 1}: biconjugate
  gradient stabilized---this is the default.

\item {\tt mg\_bottom\_solver} / {\tt hg\_bottom\_solver = 2}: conjugate
  gradient method

\item {\tt mg\_bottom\_solver} / {\tt hg\_bottom\_solver = 4}: a special 
  bottom solver that extends the range of the multigrid coarsening
  by aggregrating coarse grids on the original mesh together and
  further coarsening.

@@

\item {\tt stencil\_fill\_cc\_all\_mglevels} / {\tt stencil\_fill\_cc}:
  Compute all of the stencil coefficients
  for the Laplacian operator at all cells.  At the C-F interfaces, the
  stencil coefficients are modified to know this.

\item {\tt ml\_cc}: The main driver for the cell-centered multigrid.
   Among other things, this computes the norm that will be used
   for convergence testing.

  \item {\em recursively descend V-cycle}
\MyArrow[1em]{start1}{end1}{colorii,line width=2pt}
  \begin{itemize} 
  \item \tikzmark{end1} {\tt cc\_mg\_tower\_smoother}: Smooth the 
    problem at the current MG level using the desired smoother.

  \item {\tt compute\_defect}: Construct $f - L\phi$.

  \item\tikzmark{start1} {\tt mg\_tower\_restriction}:  Restrict
    the defect to the coarser level by conservative averaging.
  \end{itemize}

  \item {\tt mg\_tower\_bottom\_solve}:  Solve the coarsened problem
    using the chosen bottom solver.

\end{itemize}
\item {\tt compute\_defect}: This is called multiple times, checking for
   convergence at each level.

@@
